% This program and the accompanying materials are made available under the
% terms of the MIT license (X11 license) which accompanies this distribution.

% author: C. Bürger

\chapter{Bibliography}

\emph{RACR} is based on previous research in the fields of attribute grammars
and rewriting. For convenient programming, \emph{RACR} developers should be familiar with
the basic concepts of these fields. This includes attribute grammar extensions and
techniques like reference, parameterised and circular attributes and demand-driven and
incremental attribute evaluation and rewriting basics like matching and rules consisting
of left- and righ-hand sides.

To understand the advantages, in particular regarding expressiveness and complexity, of
combining attribute grammars and rewriting, it is also helpful to know basic
rewrite approaches, their limitations and relationships (term rewriting, context-free and
sensitive graph rewriting). Knowledge in programmed or strategic rewriting
may be additionally helpful to get started in the development of more complex
rewrites whose applications are steered by attributes.

The following bibliography summarises the literature most important for
\emph{RACR}. It is grouped w.r.t. attribute grammars and rewriting and respective
research problems. References are not exclusively classified; Instead references
are listed in all problem categories they are related to. To support \emph{Scheme} and
compiler construction novices, also some basic literature is given. It is highly
recommended to become used to \emph{Scheme} programming and compiler construction
concepts before looking into \emph{RACR}, attribute grammar or rewriting details. An
overview of recent and historically important attribute grammar and rewrite systems and
applications complements the bibliography.

\printbibliography[heading=subbibliography,category=Scheme,title={Scheme Programming}]

\printbibliography[heading=subbibliography,category=CompilerConstruction,title={Compiler Construction: Introduction and Basics}]

%\printbibheading[title={Attribute Grammars}]
\printbibliography[heading=subbibliography,category=AG:Foundations,title={Attribute Grammar Foundations}]
\printbibliography[heading=subbibliography,category=AG:Extensions,title={Attribute Grammar Extensions}]
\printbibliography[heading=subbibliography,category=AG:Incremental_Evaluation,title={Incremental Attribute Evaluation}]
\printbibliography[heading=subbibliography,category=AG:Systems_and_Applications,title={Attribute Grammar Systems and Applications}]

%\printbibheading[title={Graph Rewriting}]
\printbibliography[heading=subbibliography,category=GR:Foundations,title={Graph Rewriting Foundations}]
\printbibliography[heading=subbibliography,category=GR:Programmed_Graph_Rewriting,title={Programmed Graph Rewriting}]
\printbibliography[heading=subbibliography,category=GR:Systems_and_Applications,title={Graph Rewrite Systems and Applications}]